A Summery about reasoning with logic

### 2015-10-31 reasoning/summery.tex
finished with the even number of brackets.

\begin{tabular}{ll}
	Word & definition \\ \toprule
	Formula & The letters, but also letters combined with conectives (its
	recursive) \\
	Axiom & Something which is undoubtibly valid. proofs work from a
	complex formula towards axioms. \\
	Theorom & the thing you're trying to proof. \\
	Lemma & \brcell{a hypothosis which you're trying to prove, you usually
		define \\
	a lemma to reference to later. Its like a little theorom} \\
	Sequent & A thing with a sequent connective (in my case either
	$\vdash$ or $\Rightarrow$) \\
	Derivable & if X is derivable in system A, then you can proof x with
	system A
\end{tabular}

@@

\paragraph{Proof that formulas always have an even number of brackets.}
\emph{So space cowboy, we have to write a proof, before panicking remember
	the boiler plate in \autoref{structure of proofs}, we may get some
points for doing this, its at least polite}

\subparagraph{Definitions}
A formula can be a propositional variable, in which case it has zero brackets.
A formula can also be multpile proporsitional variables, connected with connectives,
in this case it has the connective count * 2 brackets, because for every connective
2 brackets are added.
\subparagraph{Strategy} Every formula has a even number of brackets, this will
be proven with help of iniduction.
\subparagraph{Proof}

>>>>

\begin{tabular}{ll}
	Jargon & Meaning\\ \toprule
	Formula & The letters, but also letters combined with conectives (its
	recursive) \\
	Axiom & \brcell{Something which is undoubtibly valid. Proofs work from a \\
	complex formula towards axioms.} \\
	Theorom & the thing you're trying to proof. \\
	Lemma & \brcell{a hypothosis which you're trying to prove, you usually
		define \\
	a lemma to reference to later. Its like a little theorom} \\
	Sequent & A thing with a sequent connective (in my case either
	$\vdash$ or $\Rightarrow$) \\
	Derivable & if X is derivable in system A, then you can proof x with
	system A
\end{tabular}

@@

\paragraph{Proof that propositional formulas always have an even number of brackets.}
\emph{So space cowboy, we have to write a proof, before panicking remember
	the boiler plate in \autoref{structure of proofs}, we may get some
points for doing this, its at least polite}

\subparagraph{Definitions}
A propositional formula can be a propositional variable,
in which case it has zero brackets.
A propositional formula can also be multpile proporsitional variables,
connected with connectives, in this case it has the connective count * 2
brackets, because for every connective 2 brackets are added.

\subparagraph{Strategy}
For all propositional formula the number of brackets is even.
This will be proven with help of iniduction.

\subparagraph{Proof}
\emph{So this is where the induction starts, first do the base case}
The base case where n = 0,
a propositional formula is a single propositional variable. This means
it has 0 brackets according to definition 1, and 0 is an even number, so
the amount of brackets in the base case is even.

\emph{Induction step}
For the case n+1, asume $A$ and $B$ have a even number of brackets,
then $A$ connective $B$ has an even number of brackets to because you have
to add an even number of brackets according to the definition of adding
connectives.

\emph{Because this can be used for the case of propositional variables,
and all complexer formulas that can be constructed with connectives, you're
done. All posibilities have been treated now.}

QED

\paragraph{Proof that all natural numbers are either odd or even}
\emph{Another quite obvious prove, but this one has a more complex induction
step, so I'll treat it here}

\subparagraph{Definitions}
Natural numbers are all integers bigger than 0.
\[Even(n) = \left\{ \begin{matrix}
	n=0 &\\ 
	Even(n-2)& 
	\end{matrix}
\right \]
